---
title: "<span style='font-size: 36px'>Regression Model Course Project</span>"
author: "Henry CY Wong"
date: "2021-03-04"
output: 
    html_document:
            css: style.css
            keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Executive Summary

The objective of this project is used to explore the relationship between a set of variables and miles per gallon (MPG) by using **mtcars** dataset and to answer:

* Is an automatic or manual transmission better for MPG
* Quantify the MPG difference between automatic and manual transmissions

As an executive summary, it could be concluded that manual transmission is 7.24 MPG better than automatic transmission in average. However, it is observed that variables  weight (**wt**), gross horsepower (**hp**), number of cylinders (**cyl**) and displacement (**disp**) also have significant relationship with MPG.

## 2. Exploratory Data Analysis

Dataset **mtcars** is loaded and explored as below:

```{r load_data}
data(mtcars)
str(mtcars)
head(mtcars, 3)
```

In order to analyze whether automatic or manual transmission is better for MPG, a boxplot is used to illustrate the correlation between **mpg** and **am** as shown in *Section 4.1* and corresponding t-test is shown below:

```{r t_test_mpg_am}
mtcars$am <- factor(mtcars$am, labels = c("Auto", "Manuel"))
t.test(mtcars[mtcars$am=="Auto",]$mpg, mtcars[mtcars$am=="Manuel",]$mpg)
```

It is observed that manual transmission is 7.24 MPG better than automatic transmission in average. The p-value is 0.001374, which is less than 0.05, indicating that it is a significant difference.

## 3. Regression Model

The Linear Model of **mpg** on **am** is

```{r model_1}
model_1 <- lm(mpg ~ am, data = mtcars)
summary(model_1)
```

It is observed that although manual transmission is better than automatic transmission in MPG, Multiple R-squared is only 0.36 which indicates that only 36% of the variance could be explained. More variables are needed to be considered.

According to the pairs plot shown in *Section 4.2*, it is observed that **cyl**, **disp**, **hp** and **wt** may have significant relationship to **mpg**. Thus, additional models are built as shown below for assessment:

```{r compose_models}
model_2 <- lm(mpg ~ am + wt + hp + cyl + disp, data = mtcars)
model_3 <- lm(mpg ~ ., data = mtcars)
```

According to the ANOVA test as shown below,
```{r anova}
anova(model_1, model_2, model_3)
```
it is observed that the p-value of **model_2** (**mpg ~ am + wt + cyl + disp + hp**) is 6.809e-07, which is less than 0.05, indicating that it is significant different compared with **model_1** (**mpg ~ am**) and **model_3** (**mpg ~ .**), respectively. 

The Linear Model of **model_2** is as shown below:

```{r show_model_2}
summary(model_2)
```
It is observed that the Multiple R-squared is 0.85 which indicates that 85% of the variance have been covered and corresponding plots for Residuals are shown in *Section 4.3*.

## 4. Appendix

### 4.1 Boxplot of mpg and am

```{r boxplot_mpg_am}
boxplot(mpg ~ am, data = mtcars, boxwex = 0.5,  ylab = "Miles Per Gallon", xlab = "Transmission Type")
```

### 4.2 Pairs Plot mtcars

```{r [pairs]}
pairs(mpg ~ ., lower.panel = panel.smooth, data = mtcars)
```

### 4.3 Residuals Plot of model_2

```{r residual}
par(mfrow = c(2, 2))
plot(model_2)
```
